MSB1015 Project

### 2024-10-17 Code/MSB1015-Project.Rmd
Update MSB1015-Project.Rmd

# Plot precision and recall
op <- par(mfrow = c(1, 2), mar = c(4, 4, 2, 2) + 0.1) # Set up the plotting layout
plot(best_class_data$best_model_overall$roc, col = "red", main = "ROC Training", las = 1) # Plot ROC curve
legend("bottomright", legend = paste0("AUC = ", signif(pROC::auc(best_class_data$best_model_overall$roc), 3)), bty = "n") # Add AUC legend
plot(best_class_data$best_model_overall$prc, col = "red", main = "Precision-recall Training") # Plot Precision-Recall curve
legend("topright", legend = paste0("AUC = ", round(best_class_data$best_model_overall$prc$auc, 3)), bty = "n") # Add AUC legend for PRC

>>>>

# Plot precision and recall
op <- par(mfrow = c(1, 2), mar = c(4, 4, 2, 2) + 0.1) # Set up the plotting layout
plot(best_class_data$best_model_overall$roc, col = "red", main = "ROC Training", las = 1) # Plot ROC curve
legend("bottomright", legend = paste0("AUC = ", signif(pROC::auc(best_class_data$best_model_overall$roc), 2)), bty = "n") # Add AUC legend
plot(best_class_data$best_model_overall$prc, col = "red", main = "Precision-recall Training") # Plot Precision-Recall curve
legend("topright", legend = paste0("AUC = ", round(best_class_data$best_model_overall$prc$auc, 2)), bty = "n") # Add AUC legend for PRC
